Running `Earth_obs_cleaning` on MCD19A2: Results from CONUS

### 2022-12-20 R/CONUS_AOD.Rmd
refine error envelope

# now with our error envelope function
system.time(envelope <- empirical.error.envelope(dt)); head(envelope)
```

>>>>

# now with our error envelope function
envelope.sat <- empirical.error.envelope(dt, pred = "y.sat") 
head(envelope.sat)

# and for the corrected data
envelope.ground.pred <- empirical.error.envelope(dt, pred = "y.ground.pred") 
head(envelope.ground.pred)
```
